% Example LaTeX document for GP111 - note % sign indicates a comment
\documentstyle[11pt]{article}
% Default margins are too wide all the way around. I reset them here
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{9in}
\setlength{\oddsidemargin}{.125in}
\setlength{\textwidth}{6.25in}
\begin{document}
\author{Cyril Allen\\
Harvard Extension School}
\renewcommand{\today}{who knows}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Workload Generation}

To verify that the work presented in this paper is improving upon the already
existing filesystem, it's necessary to generate a repeatable, synthetic
workload on the system in addition to simulations that verify the correct
behavior of the replica selection algorithm. To perform this workload
generation, I use fio[1].

\section{fio - flexible I/O tester}

fio is a tool that simulates I/O via spawning multiple threads or processes to
do a particular type of I/O action and it has the ability to generate latency
and bandwidth logs for each job [2]. Using fio removes the need to write
separate test programs for each type of workload and allows configuration via a
file that outlines the workload parameters. In addition to the convenience of
configuraiton files, fio provides a JSON output format that allows for easy
graphing of latency/bandwidth information.

\section{Test Workload Characteristics}

Testing with fio allows one to specify the workload's write pattern via a
configuration file. For this work, a simple 50\% sequential read/write pattern
will suffice as it will provide bandwidth and latency information for
simultaneous reads and writes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Test Automation}

\section{Unit Tests}

\section{Synthetic Workload Automation}
\subsection{VMware API}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{The WeightedVector Class}

It became necessary to perform repeated weighted sampling of disk IDs, given
their fitness values. An object container class was needed similar to a C++ STL
container[CITE] that can also access elements via arbitrary sampling methods.
The WeightedVector class was implemented to allow for insertion, removal, and
weighted random sampling of arbitrary objects based on their fitness values as
weights.

\subsection{Interface}

\subsection{Implementation}

\subsubsection{Sampling Techniques}

Biblio:
1. Axboe, J. (2014). Fio. urlhttp://freecode. comlprojects/fio.
2. Axboe, J., & Carroll, A. fio (1)-Linux man page. URl: http://linux. die. net/man/1/fio.
